Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Work on and merge papers

@@

\textbf{Where should we fix this bug?}\cite{kim2013should}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to aid developers in easily finding where to
    apply the necessary changes in order to fix a bug. The authors wanted to bridge
    this gap by creating a two-phase recommendation model that would locate the locations
    where the fixes need to be applied based on the corresponding bug reports.
  \item \textbf{What was the method?}
    They divided the work into multiple stages:
      \begin{itemize}
        \item firstly, they did a feature extraction on the bug reports (e.g. extract
        description, metadata, summary);
        \item in order to predict the locations of the necessary fixes, the one-phase
        recommendation model was put into place - this model would be trained on collected
        bug reports and then, when given a new bug report, it would try to localize the 
        files that need to be changed automatically;
        \item last step was to implement the two-phase recommendation model which basically
        has two classification phases - binary and multiclass:
          \begin{itemize}
            \item binary phase filters out uninformative bug reports before predicting the
            files to fix;
            \item multiclass phase where the previously filtered bug reports are used as
            training data and only after that new bug reports can be analyzed and files to be
            changed recommended.
          \end{itemize}
      \end{itemize}
  \item \textbf{What did they learn?}
    Evaluating the model yielded a 70\% accuracy in pointing to the correct files
    to be fixed, as long as the algorithm actually recommended any locations. However, the authors
    acknowledge that the approach needs extra work, especially in fine-grained defect 
    localization, performance improvement and bug triaging.
  \item \textbf{Relevance to our work}:
    The research shows interesting points regarding time-to-fix-bug and bug report
    contents, thus it can give us an insight into how ticket quality can affect that 
    time to fix the bug (in the case of this paper it would mean to successfully pass the first
    phase of the recommendation model so that fix locations could be proposed).
\end{itemize}

@@

\textbf{Towards the Next Generation of Bug Tracking Systems}\cite{just2008towards}:
\begin{itemize}
  \item \textbf{What were the goals?}
  The authors wanted to determine what makes for good bug reports and, more specifically, how the reporting environment can be changed to best suit the developers’ needs (and everyone else involved in the software project). 
  \item \textbf{What was the method?}
  They first launched a survey to developers from Eclipse, Mozilla and Apache open source projects from which they received 175 comments back. Then, they applied a card sort in order to organize the comments into hierarchies to deduce a higher level of abstraction and identify common patterns. 
  \item \textbf{What did they learn?}
  They found 7 main topics of improvement for bug tracking systems: provide tool support for users to collect and prepare information that developers need, find volunteers to translate bug reports filed in foreign languages, provide different user interfaces for each user level and give cues to inexperienced reporters on what to report and best practices, reward reporters when they do a good job, integrate reputation into user profiles to mark experienced reporters, provide powerful and easy to use tools to search bug reports, encourage users to submit additional details (provide tools for merging bugs). 
  \item \textbf{Relevance to our work}:
  This is an important paper to our research as it presents, from open source developers’ perspective, how bug reporting and bug tracking systems should behave. This research gives us various topics to concentrate on when analyzing the quality of tickets. 
\end{itemize}

>>>>

However, \citet{kim2013should} propose a rather different technique than the one
exposed in \citet{bettenburg2012using}. The authors have employed a two-phase
recommendation model that would locate the necessary fixes based on information
in bug reports. Firstly, they did a feature extraction on the bug reports (e.g. 
extract description, summary, metadata). Then, in order to successfully predict
locations, this model was trained on collected bug reports and then, when given
a new bug report, it would try to localize the files that need to be changed 
automatically. Finally, the actual implementation was put into place, and that
is the two phase recommendation model, composed of binary (filters out 
uninformative bug reports before predicting the files to fix) and multiclass (
previously filtered bug reports are used as training data and only after that
new bug reports can be analyzed and files to be changed recommended). The 
overall accuracy was above the one achieved by \citet{bettenburg2012using}, 
being able to rank over 70\%, but only as long as it recommended \emph{any} 
locations.

Even though we have discussed about quality in bug reports and how it can be
identified, we must also investigate if the platform where these bug reports 
reside (i.e. bug trackers) are properly fitting the software environment. 
The work of \citet{just2008towards} tries to find the answer to this question.
The authors launched a survey to developers from Eclipse, Mozilla and Apache
open source projects from which they received 175 comments back. Then, they
applied a card sort in order to organize the comments into hierarchies to 
deduce a higher level of abstraction and identify common patterns. In the end,
they ranked the top suggestions as follows:
  \begin{itemize}
    \item provide tool support for users to collect and prepare information that 
      developers need;
    \item find volunteers to translate bug reports filed in foreign languages;
    \item provide different user interfaces for each user level and give cues to 
      inexperienced reporters on what to report and best practices;
    \item reward reporters when they do a good job;
    \item integrate reputation into user profiles to mark experienced reporters;
    \item provide powerful and easy to use tools to search bug reports;
    \item encourage users to submit additional details (provide tools for merging 
      bugs).
  \end{itemize}

One other important aspect when analyzing the quality of a bug report is the
time it takes to triage it. Triaging is the process of analyzing issues and 
based on the information available, assign it to

@@

@@
